---
title: "Data science"
format: html
editor: visual
---
# 1. Questions

## 1.1 What do you think being a data scientist is about?

Being a data scientist is about harnessing the power of data to drive decision-making and innovation. It requires a blend of technical skills, domain knowledge, and the ability to communicate complex ideas effectively.

## 1.2 What differences/similarities do you see between data scientists and statisticians?

While data scientists and statisticians both work with data to derive insights, data scientists have a broader skill set that includes programming, machine learning, and data engineering. Statisticians, on the other hand, have a more focused expertise in statistical methods and theory. The role of a data scientist is often more interdisciplinary, blending statistical analysis with advanced computational techniques and domain-specific knowledge.

## 1.3 How do you view yourself in relation to these two areas?

As I have strong background of programming skills, but weak on statistical theory, I prefer to pursue my career be data scientist.


# 2. R code

```{r}
y <- density(iris$Sepal.Length)
class(y)
typeof(y)
str(y)
```

The code chunk above is used to determine the class, type, and structure of the object y.

```{r}
#| echo: false
plot(y)
```

The code chunk above is used to plot the objective y.
The `echo: false` option disables the printing of code (only output is displayed).
